A new method to estimate dark matter halo concentrations

### 2015-04-22 paper/article.tex
finished first pass on in the introduction

@@

In this paper we propose a new method to estimate the dark matter halo
concentration from N-body simulation results. This method has two
advantages with respect to the methods mentioned above. First, it does
not involve data binning. Second, it does not throw away data
points. Third, it allows for an straightforward estimation of the
uncertainties in the concentration parameter.

Our method consists in building the cumulative mass profile from the
particle data in the N-body simulation to find the best possible
concentration value using a Markov Chain Monte Carlo methodology by
comparing the data against the analytic expectation.

This paper is structured as follows. In Section \ref{sec:basics} we
review the basic properties of the NFW density profile and define the
basic notation for the rest of the paper. Next in Section
\ref{sec:method} we present our new method to estimate the halo
concentration, paying special attention to the Bayesian framework to
find the most probable value and its uncertainty. In Section
\ref{sec:results} we demonstrate the power of our method with two
different halo samples; the first one generated under controlled
conditions and the second taken from a cosmological N-body
simulation to comment on the consequences for the concentration-mass
relationship. We present our conclusions in Section
\ref{sec:conclusions}.

>>>>

In this paper we propose a new method to estimate the dark matter halo
concentration in halos obtained in numerical simulations. 
It consists in building the cumulative mass profile from the
particle data in the N-body simulation to find the best possible
concentration value using a Markov Chain Monte Carlo (MCMC)
methodology by comparing the data against the analytic expectation.

Our proposal has two advantages with respect to the two methods mentioned
above. 
First, it does not involve data binning. 
Second, it does not throw away data points. 
Furthermore, the MCMC approach allows for an straightforward
estimation of the uncertainties in the concentration parameter, and
inclusion of informative priors.

@@
